---
title: "getting Started with trophToxNTO"
author: "Haute Heure et al."
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

This vignette presents the installation and the basic use of functions included in the package `trophToxNTO`.

## Installation

```{r, eval=FALSE}
install.packages('devtools') # if not already installed
library('devtools') # load the library
github_install("vbaudrot/trophToxNTO/trophToxNTO") # install from 'master'
```

And then, simply load the package :
```{r loadLibrary}
library(trophToxNTO)
```

## Step by step presentation

1. If not yet done, first of all, load the package `EUMSCAProject`:

2. Describe the scenario: give he level of broma require for treatment, `vole.level.test` in individual, and the quantity of treatment input, `broma.level.test` , in ppm.

```{r,warning=FALSE}
vole.level.test = 250
broma.level.test = 20*50

# Run condition function for scenario
scenario = condition(Vole.Level=vole.level.test,Broma.Level=broma.level.test)

root.event=scenario[[1]]
event.func=scenario[[2]]
```

3. Integration of the differential equation system

In the part, you need first to download package `deSolve`, then the number of parallel simulation is require for the integration (use the pars function to avoid confusion).

Here is for 1 simulations

```{r ode1, warning=FALSE, cache=TRUE}
# Load package deSolve
# library(deSolve)

# number of parallel simulation
params=pars(n=1)

# times vector of integration
times <- seq(from=0, to=15*365, length.out = 1e3) #  30*5 = 5 months 

# Run the model

model.output    <- ode(times = times,
                       y = init(params$n),
                       func = ode.broma.tritrophic,
                       parms  = params,
                       events = list(func = event.func, root = TRUE),
                       rootfun = root.event)

```

4. Graphic output

```{r,warning=FALSE,message=FALSE}
graphique(params$n,times,model.output) 
```

## Test multi-parameters

Several simulation in parallele to test parameters. Here it's the carrying capacity of voles `K.V`.

```{r, warning=FALSE, cache = TRUE}
# number of parallel simulation
params=pars(n=2)

# Run the model
model.output    <- ode(times = times,
                       y = init(params$n),
                       func = ode.broma.tritrophic,
                       parms = pars(
                         n=params$n, # Do not foret to specify this !!!
                         K.V=seq(200,800,length=params$n)
                       ),
                       events = list(func = event.func, root = TRUE),
                       rootfun = root.event)

# Graphic output
graphique(params$n,times,model.output) 
```

## Test multi initial values

Several simulation in parallele with different initial conditions. Here for foxes, $0$ and $0.03$ ind/ha. 


```{r,warning=FALSE, cache=TRUE}
# number of parallel simulation
params=pars(n=2)

# Run the model
model.output    <- ode(times = times,
                       y = init(params$n,
                                D.F = c(0,0.2)
                                ),
                       func = ode.broma.tritrophic,
                       parms = params,
                       events = list(func = event.func, root = TRUE),
                       rootfun = root.event)

# Graphic output
graphique(params$n,times,model.output) 
```

## Test multi parameters and multi initial values

| group | $Fx$ | $K.V$ |
|---|---|---|
| 1 | 0 | 400 | 
| 2 | 0.03 | 600 |
| 3 | 0 | 600 |
| 4 | 0.03 | 400 |

```{r,warning=FALSE, cache=TRUE}
# number of parallel simulation
params=pars(n=4)

# Run the model
model.output    <- ode(times = times,
                       y = init(params$n,
                                D.F = c(0,0.03,0,0.03)
                                ),
                       func = ode.broma.tritrophic,
                       parms = pars(
                         n=params$n, # Do not foret to specify this !!!
                         K.V=c(400,600,600,400)
                       ),
                       events = list(func = event.func, root = TRUE),
                       rootfun = root.event)

# Graphic output
graphique(params$n,times,model.output) 
```

## Graphique_3 : Another graphique reduce compared to graphique()

```{r,warning=FALSE}
graphique_3(params$n,times,model.output) 
```


## Graphique_2 : simulation with and without foxes

```{r,warning=FALSE, cache=TRUE}
times <- seq(from=0, to=15*365, length.out = 1e4) #  30*5 = 5 months 

params=pars(n=2,
            LD.50.F=0.5,
            days.to.die.F=5
            )

init.p=init(params$n,
     D.F = c(0,0.025)
     )

# --------------------------- EVENEMENTS -------------------
scenario=condition(Vole.Level=250,Broma.Level=20*50)
root.event=scenario[[1]]
event.func=scenario[[2]]

# --------------------------- Modelisation -------------------
model.output = ode(y=init.p,
                   times,
                   ode.broma.tritrophic, 
                   parms = params,
                   events = list(func = event.func, root = TRUE),
                   rootfun = root.event)

# --------------------------- Plot-------------------
graphique_2(params$n,times,model.output)
```

## Output Ingestion and Mortality


####  Model for test

```{r,warning=FALSE, cache=TRUE}
params=pars(n=1,
            LD.50.F=0.5,
            days.to.die.F=5)

# times vector of integration
times <- seq(from=0, to=30*365, length.out = 1e4) #  30*5 = 5 months 

scenario=condition(Vole.Level=500,Broma.Level=20*50)
root.event=scenario[[1]]
event.func=scenario[[2]]

model.output    <- ode(times = times,
                       y = init(params$n),
                       func = ode.broma.tritrophic,
                       parms  = params,
                       events = list(func = event.func, root = TRUE),
                       rootfun = root.event)


df=table_df(model.output)
```

### Repartition of ingestion in mustelids and foxes

```{r,warning=FALSE}
# library(gridExtra) # to plot grid.arrange()
```


```{r,warning=FALSE}
# df.Nbr.ingest=Nbr.ingest(df,params,group.num=1)
# 
# p.ingest=plotIngest(df.Nbr.ingest)
# 
# ingestion.mustelids=p.ingest[[1]]
# ingestion.foxes=p.ingest[[2]]
# 
# grid.arrange(ingestion.mustelids,ingestion.foxes,nrow=2)
```

### Repartition of mortality in Voles and Mustelids

```{r,warning=FALSE}
# df.Nbr.mortality=Nbr.mortality(df,params,group.num=1)
# 
# p.mortality=plotMortality(df.Nbr.mortality)
# 
# mortality.voles=p.mortality[[1]]
# mortality.mustelids=p.mortality[[2]]
# 
# grid.arrange(mortality.voles,mortality.mustelids,nrow=2)
```


