---
title: "Simulations"
author: "Haute Heure et al."
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---


```{r,echo=FALSE,warning=FALSE,include=FALSE}
knitr::opts_chunk$set(fig.height = 6,
                      fig.width = 7)

library(trophToxNTO) # Package for ordinary differential equations
library(gridExtra)
```


```{r param,echo=FALSE,warning=FALSE,include=FALSE}
times <- seq(from=0, to = 50*365, length = 50*365) #  30*5 = 5 months 

params <- pars(n=1)

init.p <- init(params$n)
```

# With foxes

----------------------------------------- CONTROL

## a) Model 0-0


```{r model.output_0.0, echo=FALSE,warning=FALSE,comment=FALSE,message=FALSE, cache=TRUE}
# --------------------------- Modelisation -------------------
model.output_0.0 = ode(y=init.p,
                    times,
                    ode.broma.tritrophic, 
                    parms = params)
# --------------------------- Plot-------------------
graph_0.0 <- graphique_3(params$n,times,model.output_0.0)
```

## b) Model 500-20

```{r model.output_500.20, cache=TRUE}
# --------------------------- EVENEMENTS -------------------
root.event=condition(Vole.Level=500,Broma.Level=20*50)[[1]] # kg * mg/kg
event.func=condition(Vole.Level=500,Broma.Level=20*50)[[2]]

# --------------------------- Modelisation -------------------
model.output_500.20 = ode(y=init.p,
                   times,
                   ode.broma.tritrophic, 
                   parms = params,
                   events = list(func = event.func, root = TRUE),
                   rootfun = root.event)

graph_500.20 <- graphique_3(params$n,times,model.output_500.20)
```


## c) Model 250-20

```{r model.output_250.20, cache=TRUE}
# --------------------------- EVENEMENTS -------------------
root.event = condition(Vole.Level=250,Broma.Level=20*50)[[1]]
event.func = condition(Vole.Level=250,Broma.Level=20*50)[[2]]

# --------------------------- Modelisation -------------------
model.output_250.20 = ode(y=init.p,
                   times,
                   ode.broma.tritrophic, 
                   parms = params,
                   events = list(func = event.func, root = TRUE),
                   rootfun = root.event)

graph_250.20 <- graphique_3(params$n,times,model.output_250.20)
```

## d) Model 250-7.5

```{r model.output_250.7.5, cache=TRUE}
# --------------------------- EVENEMENTS -------------------
root.event = condition(Vole.Level=250,Broma.Level=7.5*50)[[1]]
event.func = condition(Vole.Level=250,Broma.Level=7.5*50)[[2]]

# --------------------------- Modelisation -------------------
model.output_250.7.5 = ode(y=init.p,
                   times,
                   ode.broma.tritrophic, 
                   parms = params,
                   events = list(func = event.func, root = TRUE),
                   rootfun = root.event)
graph_250.7.5 <-graphique_3(params$n,times,model.output_250.7.5)
```

## e) Model 50-7.5

```{r model.output_50.7.5, cache=TRUE}
# --------------------------- EVENEMENTS -------------------
root.event = condition(Vole.Level=50,Broma.Level=7.5*50)[[1]]
event.func = condition(Vole.Level=50,Broma.Level=7.5*50)[[2]]

# --------------------------- Modelisation -------------------
model.output_50.7.5 = ode(y = init.p,
                   times,
                   ode.broma.tritrophic, 
                   parms = params,
                   events = list(func = event.func, root = TRUE),
                   rootfun = root.event)

graph_50.7.5 <- graphique_3(params$n,times,model.output_50.7.5)
```


# Without foxes

```{r, cache=TRUE}
init.p <- init(params$n, D.F=0)
```


## a) Model 0-0


```{r model.output_0.0_0F, echo=FALSE,warning=FALSE,comment=FALSE,message=FALSE, cache=TRUE}
# --------------------------- Modelisation -------------------
model.output_0.0_0F = ode(y=init.p,
                    times,
                    ode.broma.tritrophic, 
                    parms = params)
# --------------------------- Plot-------------------
graph_0.0_0F <-  graphique_3(params$n,times,model.output_0.0_0F)
```

## b) Model 500-20

```{r model.output_500.20_0F, cache=TRUE}
# --------------------------- EVENEMENTS -------------------
root.event=condition(Vole.Level=500,Broma.Level=20*50)[[1]]
event.func=condition(Vole.Level=500,Broma.Level=20*50)[[2]]

# --------------------------- Modelisation -------------------
model.output_500.20_0F = ode(y=init.p,
                   times,
                   ode.broma.tritrophic, 
                   parms = params,
                   events = list(func = event.func, root = TRUE),
                   rootfun = root.event)

graph_500.20_0F <- graphique_3(params$n,times,model.output_500.20_0F)
```


## c) Model 250-20

```{r model.output_250.20_0F, cache=TRUE}
# --------------------------- EVENEMENTS -------------------
root.event = condition(Vole.Level=250,Broma.Level=20*50)[[1]]
event.func = condition(Vole.Level=250,Broma.Level=20*50)[[2]]

# --------------------------- Modelisation -------------------
model.output_250.20_0F = ode(y=init.p,
                   times,
                   ode.broma.tritrophic, 
                   parms = params,
                   events = list(func = event.func, root = TRUE),
                   rootfun = root.event)

graph_250.20_0F <-graphique_3(params$n,times,model.output_250.20_0F)
```

## d) Model 250-7.5

```{r model.output_250.7.5_0F, cache=TRUE}
# --------------------------- EVENEMENTS -------------------
root.event = condition(Vole.Level=250,Broma.Level=7.5*50)[[1]]
event.func = condition(Vole.Level=250,Broma.Level=7.5*50)[[2]]

# --------------------------- Modelisation -------------------
model.output_250.7.5_0F = ode(y=init.p,
                   times,
                   ode.broma.tritrophic, 
                   parms = params,
                   events = list(func = event.func, root = TRUE),
                   rootfun = root.event)

graph_250.7.5_0F <- graphique_3(params$n,times,model.output_250.7.5_0F)
```

## e) Model 50-7.5

```{r model.output_50.7.5_0F, cache=TRUE}
# --------------------------- EVENEMENTS -------------------
root.event = condition(Vole.Level=50,Broma.Level=7.5*50)[[1]]
event.func = condition(Vole.Level=50,Broma.Level=7.5*50)[[2]]

# --------------------------- Modelisation -------------------
model.output_50.7.5_0F = ode(y = init.p,
                   times,
                   ode.broma.tritrophic, 
                   parms = params,
                   events = list(func = event.func, root = TRUE),
                   rootfun = root.event)

graph_50.7.5_0F <- graphique_3(params$n,times,model.output_50.7.5_0F)
```

# MEASURE OUTPUT

## with foxes

```{r}
tab_sensitivity(model.output_0.0, params)[,36:42]
tab_sensitivity(model.output_500.20, params)[,36:42]
tab_sensitivity(model.output_250.20, params)[,36:42]
tab_sensitivity(model.output_250.7.5, params)[,36:42]
tab_sensitivity(model.output_5.7.5, params)[,36:42]
```

## without foxes

```{r}
tab_sensitivity(model.output_0.0_0F, params)[,36:42]
tab_sensitivity(model.output_500.20_0F, params)[,36:42]
tab_sensitivity(model.output_250.20_0F, params)[,36:42]
tab_sensitivity(model.output_250.7.5_0F, params)[,36:42]
tab_sensitivity(model.output_5.7.5_0F, params)[,36:42]
```


# EXPORT GRAPHICS

```{r}
# setwd("~/Documents/PACKAGES/trophToxNTO/trophToxNTO")
# save(model.output_0.0, file = "data/model.output_0.0.rda")
# save(model.output_500.20, file = "data/model.output_500.20.rda")
# save(model.output_250.20, file = "data/model.output_250.20.rda")
# save(model.output_250.7.5, file = "data/model.output_250.7.5.rda")
# save(model.output_50.7.5, file = "data/model.output_50.7.5_0F.rda")
# 
# save(model.output_0.0_0F, file = "data/model.output_0.0_0F.rda")
# save(model.output_500.20_0F, file = "data/model.output_500.20_0F.rda")
# save(model.output_250.20_0F, file = "data/model.output_250.20_0F.rda")
# save(model.output_250.7.5_0F, file =  "data/model.output_250.7.5_0F.rda")
# save(model.output_50.7.5_0F, file = "data/model.output_50.7.5_0F.rda")
```

```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
# setwd("~/Documents/PACKAGES/trophToxNTO/trophToxNTO")
# load(file = "data/model.output_0.0.rda")
# load(file = "data/model.output_500.20.rda")
# load(file = "data/model.output_250.20.rda")
# load(file = "data/model.output_250.7.5.rda")
# load(file = "data/model.output_50.7.5_0F.rda")
# 
# load(file = "data/model.output_0.0_0F.rda")
# load(file = "data/model.output_500.20_0F.rda")
# load(file = "data/model.output_250.20_0F.rda")
# load(file =  "data/model.output_250.7.5_0F.rda")
# load(file = "data/model.output_50.7.5_0F.rda")
```


```{r}
# With Foxes

ggsave(filename = "../manuscript/img/graph_0_0.png", plot = graph_0.0,
       width = 7, height = 9)

ggsave(filename = "../manuscript/img/graph_500_20.png", plot = graph_500.20,
       width = 7, height = 9)

ggsave(filename = "../manuscript/img/graph_250_20.png", plot = graph_250.20,
       width = 7, height = 9)

ggsave(filename = "../manuscript/img/graph_250_7_5.png", plot = graph_250.7.5,
       width = 7, height = 9)

ggsave(filename = "../manuscript/img/graph_50_7_5.png", plot = graph_50.7.5,
       width = 7, height = 9)

# Without Foxes
ggsave(filename = "../manuscript/img/graph_0_0_0F.png", plot = graph_0.0_0F,
       width = 7, height = 9)

ggsave(filename = "../manuscript/img/graph_500_20_0F.png", plot = graph_500.20_0F,
       width = 7, height = 9)

ggsave(filename = "../manuscript/img/graph_250_20_0F.png", plot = graph_250.20_0F,
       width = 7, height = 9)

ggsave(filename = "../manuscript/img/graph_250_7_5_0F.png", plot = graph_250.7.5_0F,
       width = 7, height = 9)

ggsave(filename = "../manuscript/img/graph_50_7_5_0F.png", plot = graph_50.7.5_0F,
       width = 7, height = 9)
```

## With foxes


### Foxes and Mustelids


```{r}
## INITIAL VALUE
# scale_fun_F <- function(df){
#   df[df$time == 0, "D.F_"]
# }
# scale_fun_M <- function(df){
#   df[df$time == 0, "D.M_"]
# }
## SCALE WITH MAXIMAL
scale_fun_F <- function(df){
  max(df$D.F_)
}
scale_fun_M <- function(df){
  max(df$D.M_)
}
```


```{r}
df_tab <- as.data.frame(model.output_0.0) %>%
  select(time, D.F_, D.M_) %>%
  mutate(group = "0.0",
         ID_group = "a")
D.F_scale_0.0 = scale_fun_F(df_tab)
D.M_scale_0.0 = scale_fun_M(df_tab)

df_tab$Foxes = df_tab$D.F_ / D.F_scale_0.0
df_tab$Mustelids = df_tab$D.M_ / D.M_scale_0.0

plot(df_tab$time, df_tab$Foxes)
plot(df_tab$time, df_tab$Mustelids)

df_plot_0.0_MF <- df_tab %>%
  gather(Species, ratioVar, c('Foxes', 'Mustelids'))

plot_0.0_MF <- ggplot(data = df_plot_0.0_MF) + theme_minimal() +
  scale_x_continuous(
      breaks = seq(0,max(times),length=11),
      labels=round(seq(0,max(times)/365,length=11),1),
      name="time in year")+
  scale_color_manual(values = c("black", "grey70")) +
  labs(y = "Rate of variation of densities") +
  geom_line(aes(x = time, y = ratioVar, color = Species))
plot_0.0_MF
```

```{r}
df_tab <- as.data.frame(model.output_500.20) %>%
  select(time, D.F_, D.M_) %>%
  mutate(group = "500.20",
         ID_group = "b")
D.F_scale_500.20 = scale_fun_F(df_tab)
D.M_scale_500.20 = scale_fun_M(df_tab)

df_tab$Foxes = df_tab$D.F_ / D.F_scale_500.20
df_tab$Mustelids = df_tab$D.M_ / D.M_scale_500.20

plot(df_tab$time, df_tab$Foxes)
plot(df_tab$time, df_tab$Mustelids)

df_plot_500.20_MF <- df_tab %>%
  gather(Species, ratioVar, c('Foxes', 'Mustelids'))

plot_500.20_MF <- ggplot(data = df_plot_500.20_MF) + theme_minimal() +
  scale_x_continuous(
      breaks = seq(0,max(times),length=11),
      labels=round(seq(0,max(times)/365,length=11),1),
      name="time in year")+
  scale_color_manual(values = c("black", "grey70")) +
  labs(y = "Rate of variation of densities") +
  geom_line(aes(x = time, y = ratioVar, color = Species))
plot_500.20_MF
```


```{r}
df_tab <- as.data.frame(model.output_250.20) %>%
  select(time, D.F_, D.M_) %>%
  mutate(group = "250.20",
         ID_group = "c")
D.F_scale_250.20 = scale_fun_F(df_tab)
D.M_scale_250.20 = scale_fun_M(df_tab)

df_tab$Foxes = df_tab$D.F_ / D.F_scale_250.20
df_tab$Mustelids = df_tab$D.M_ / D.M_scale_250.20

plot(df_tab$time, df_tab$Foxes)
plot(df_tab$time, df_tab$Mustelids)

df_plot_250.20_MF <- df_tab %>%
  gather(Species, ratioVar, c('Foxes', 'Mustelids'))

plot_250.20_MF <- ggplot(data = df_plot_250.20_MF) + theme_minimal() +
  scale_x_continuous(
      breaks = seq(0,max(times),length=11),
      labels=round(seq(0,max(times)/365,length=11),1),
      name="time in year")+
  scale_color_manual(values = c("black", "grey70")) +
  labs(y = "Rate of variation of densities") +
  geom_line(aes(x = time, y = ratioVar, color = Species))
plot_250.20_MF
```


```{r}
df_tab <- as.data.frame(model.output_250.7.5) %>%
  select(time, D.F_, D.M_) %>%
  mutate(group = "250.7.5",
         ID_group = "d")
D.F_scale_250.7.5 = scale_fun_F(df_tab)
D.M_scale_250.7.5 = scale_fun_M(df_tab)

df_tab$Foxes = df_tab$D.F_ / D.F_scale_250.7.5
df_tab$Mustelids = df_tab$D.M_ / D.M_scale_250.7.5

plot(df_tab$time, df_tab$Foxes)
plot(df_tab$time, df_tab$Mustelids)

df_plot_250.7.5_MF <- df_tab %>%
  gather(Species, ratioVar, c('Foxes', 'Mustelids'))

plot_250.7.5_MF <- ggplot(data = df_plot_250.7.5_MF) + theme_minimal() +
  scale_x_continuous(
      breaks = seq(0,max(times),length=11),
      labels=round(seq(0,max(times)/365,length=11),1),
      name="time in year")+
  scale_color_manual(values = c("black", "grey70")) +
  labs(y = "Rate of variation of densities") +
  geom_line(aes(x = time, y = ratioVar, color = Species))
plot_250.7.5_MF
```

```{r}
df_tab <- as.data.frame(model.output_50.7.5) %>%
  select(time, D.F_, D.M_) %>%
  mutate(group = "50.7.5",
         ID_group = "e")
D.F_scale_50.7.5 = scale_fun_F(df_tab)
D.M_scale_50.7.5 = scale_fun_M(df_tab)

df_tab$Foxes = df_tab$D.F_ / D.F_scale_50.7.5
df_tab$Mustelids = df_tab$D.M_ / D.M_scale_50.7.5

plot(df_tab$time, df_tab$Foxes)
plot(df_tab$time, df_tab$Mustelids)

df_plot_50.7.5_MF <- df_tab %>%
  gather(Species, ratioVar, c('Foxes', 'Mustelids'))

plot_50.7.5_MF <- ggplot(data = df_plot_50.7.5_MF) + theme_minimal() +
  scale_x_continuous(
      breaks = seq(0,max(times),length=11),
      labels=round(seq(0,max(times)/365,length=11),1),
      name="time in year")+
  scale_color_manual(values = c("black", "grey70")) +
  labs(y = "Rate of variation of densities") +
  geom_line(aes(x = time, y = ratioVar, color = Species))
plot_50.7.5_MF
```

### Vole and Dead Vole

```{r}
## INITIAL VALUE
# scale_fun_Vd <- function(df){
#   df[df$time == 0, "D.Vd_"]
# }
# scale_fun_V <- function(df){
#   df[df$time == 0, "D.V_"]
# }
## SCALE WITH VAXIVAL
scale_fun_Vd <- function(df){
  max(df$D.Vd_)
}
scale_fun_V <- function(df){
  max(df$D.V_)
}
```



```{r}
df_tab <- as.data.frame(model.output_0.0) %>%
  select(time, D.Vd_, D.V_) %>%
  mutate(group = "0.0",
         ID_group = "a")
D.Vd_scale_0.0 = scale_fun_Vd(df_tab)
D.V_scale_0.0 = scale_fun_V(df_tab)

df_tab$dead_Voles = df_tab$D.Vd_ / D.Vd_scale_0.0
df_tab$Voles = df_tab$D.V_ / D.V_scale_0.0

plot(df_tab$time, df_tab$Voles)
plot(df_tab$time, df_tab$Voles)

df_plot_0.0_VVd <- df_tab %>%
  gather(Species, ratioVar, c('dead_Voles', 'Voles'))

plot_0.0_VVd <- ggplot(data = df_plot_0.0_VVd) + theme_minimal() +
  scale_x_continuous(
      breaks = seq(0,max(times),length=11),
      labels=round(seq(0,max(times)/365,length=11),1),
      name="time in year")+
  scale_color_manual(values = c("black", "grey70")) +
  labs(y = "Rate of variation of densities") +
  geom_line(aes(x = time, y = ratioVar, color = Species))
plot_0.0_VVd
```

```{r}
df_tab <- as.data.frame(model.output_500.20) %>%
  select(time, D.Vd_, D.V_) %>%
  mutate(group = "500.20",
         ID_group = "b")
D.Vd_scale_500.20 = scale_fun_Vd(df_tab)
D.V_scale_500.20 = scale_fun_V(df_tab)

df_tab$dead_Voles = df_tab$D.Vd_ / D.Vd_scale_500.20
df_tab$Voles = df_tab$D.V_ / D.V_scale_500.20

plot(df_tab$time, df_tab$dead_Voles)
plot(df_tab$time, df_tab$Voles)

df_plot_500.20_VVd <- df_tab %>%
  gather(Species, ratioVar, c('dead_Voles', 'Voles'))

plot_500.20_VVd <- ggplot(data = df_plot_500.20_VVd) + theme_minimal() +
  scale_x_continuous(
      breaks = seq(0,max(times),length=11),
      labels=round(seq(0,max(times)/365,length=11),1),
      name="time in year")+
  scale_color_manual(values = c("black", "grey70")) +
  labs(y = "Rate of variation of densities") +
  geom_line(aes(x = time, y = ratioVar, color = Species))
plot_500.20_VVd
```


```{r}
df_tab <- as.data.frame(model.output_250.20) %>%
  select(time, D.Vd_, D.V_) %>%
  mutate(group = "250.20",
         ID_group = "c")
D.Vd_scale_250.20 = scale_fun_Vd(df_tab)
D.V_scale_250.20 = scale_fun_V(df_tab)

df_tab$dead_Voles = df_tab$D.Vd_ / D.Vd_scale_250.20
df_tab$Voles = df_tab$D.V_ / D.V_scale_250.20

plot(df_tab$time, df_tab$dead_Voles)
plot(df_tab$time, df_tab$Voles)

df_plot_250.20_VVd <- df_tab %>%
  gather(Species, ratioVar, c('dead_Voles', 'Voles'))

plot_250.20_VVd <- ggplot(data = df_plot_250.20_VVd) + theme_minimal() +
  scale_x_continuous(
      breaks = seq(0,max(times),length=11),
      labels=round(seq(0,max(times)/365,length=11),1),
      name="time in year")+
  scale_color_manual(values = c("black", "grey70")) +
  labs(y = "Rate of variation of densities") +
  geom_line(aes(x = time, y = ratioVar, color = Species))
plot_250.20_VVd
```


```{r}
df_tab <- as.data.frame(model.output_250.7.5) %>%
  select(time, D.Vd_, D.V_) %>%
  mutate(group = "250.7.5",
         ID_group = "d")
D.Vd_scale_250.7.5 = scale_fun_Vd(df_tab)
D.V_scale_250.7.5 = scale_fun_V(df_tab)

df_tab$dead_Voles = df_tab$D.Vd_ / D.Vd_scale_250.7.5
df_tab$Voles = df_tab$D.V_ / D.V_scale_250.7.5

plot(df_tab$time, df_tab$dead_Voles)
plot(df_tab$time, df_tab$Voles)

df_plot_250.7.5_VVd <- df_tab %>%
  gather(Species, ratioVar, c('dead_Voles', 'Voles'))

plot_250.7.5_VVd <- ggplot(data = df_plot_250.7.5_VVd) + theme_minimal() +
  scale_x_continuous(
      breaks = seq(0,max(times),length=11),
      labels=round(seq(0,max(times)/365,length=11),1),
      name="time in year")+
  scale_color_manual(values = c("black", "grey70")) +
  labs(y = "Rate of variation of densities") +
  geom_line(aes(x = time, y = ratioVar, color = Species))
plot_250.7.5_VVd
```

```{r}
df_tab <- as.data.frame(model.output_50.7.5) %>%
  select(time, D.Vd_, D.V_) %>%
  mutate(group = "50.7.5",
         ID_group = "e")
D.Vd_scale_50.7.5 = scale_fun_Vd(df_tab)
D.V_scale_50.7.5 = scale_fun_V(df_tab)

df_tab$dead_Voles = df_tab$D.Vd_ / D.Vd_scale_50.7.5
df_tab$Voles = df_tab$D.V_ / D.V_scale_50.7.5

plot(df_tab$time, df_tab$dead_Voles)
plot(df_tab$time, df_tab$Voles)

df_plot_50.7.5_VVd <- df_tab %>%
  gather(Species, ratioVar, c('dead_Voles', 'Voles'))

plot_50.7.5_VVd <- ggplot(data = df_plot_50.7.5_VVd) + theme_minimal() +
  scale_x_continuous(
      breaks = seq(0,max(times),length=11),
      labels=round(seq(0,max(times)/365,length=11),1),
      name="time in year")+
  scale_color_manual(values = c("black", "grey70")) +
  labs(y = "Rate of variation of densities") +
  geom_line(aes(x = time, y = ratioVar, color = Species))
plot_50.7.5_VVd
```

### Plots and join plot


```{r}
# legend.position = c(.5, .5))
# z + theme(legend.background = element_rect(colour = "black")
plot_join <- ggplot() +
  theme_minimal() +
  theme(legend.position = c(0.13, 0.93), # c(0,0) bottom left, c(1,1) top-right.
        legend.background = element_rect(fill = "#ffffffaa", colour = NA),
        legend.title = element_blank()
  ) +
  # theme(legend.position="none") +
  scale_x_continuous(
      breaks = seq(0,max(times),length=11),
      labels=round(seq(0,max(times)/365,length=11),1),
      name="Time in year")+
  scale_color_manual(values = c("black", "grey50")) +
  labs(y = "Rate of variation of densities") +
  # Buffer
  geom_rect(
    data=data.frame(ID_group = c("a", "b", "c", "d", "e")),
    aes(xmin=0, xmax=365*10, ymin=-Inf, ymax=Inf), 
    alpha = 0.5, fill = 'grey')

y_min = -Inf # 1 
y_max = Inf # 1.2

b_seq = 365*c(10,   14.5,16.1,    21.2,22.9,   28,29.5,   34.9,36.5,   41.6,43.3,   48.3,50)
d_seq = 365*c(10,12.2,  14.8,17,  20.5,24, 27.2,30.4,   33.2,35.6,   39,42.7,  45.5,47.9,  50)
# VR Regulation
plot_join <- plot_join +
  geom_rect(data=data.frame(ID_group = "a"),
            aes(xmin=365*10, xmax=365*50, ymin=y_min, ymax=y_max),
            alpha = 0.5, fill = '#75E4E4') +
  # b
  geom_rect(data=data.frame(ID_group = "b"),
            aes(xmin=b_seq[1], xmax=b_seq[2], ymin=y_min, ymax=y_max),
            alpha = 0.5, fill = '#75E4E4') +
  geom_rect(data=data.frame(ID_group = "b"),
            aes(xmin=b_seq[3], xmax=b_seq[4], ymin=y_min, ymax=y_max),
            alpha = 0.5, fill = '#75E4E4') +
  geom_rect(data=data.frame(ID_group = "b"),
            aes(xmin=b_seq[5], xmax=b_seq[6], ymin=y_min, ymax=y_max),
            alpha = 0.5, fill = '#75E4E4') +
  geom_rect(data=data.frame(ID_group = "b"),
            aes(xmin=b_seq[7], xmax=b_seq[8], ymin=y_min, ymax=y_max),
            alpha = 0.5, fill = '#75E4E4') +
  geom_rect(data=data.frame(ID_group = "b"),
            aes(xmin=b_seq[9], xmax=b_seq[10], ymin=y_min, ymax=y_max),
            alpha = 0.5, fill = '#75E4E4') +
  geom_rect(data=data.frame(ID_group = "b"),
            aes(xmin=b_seq[11], xmax=b_seq[12], ymin=y_min, ymax=y_max),
            alpha = 0.5, fill = '#75E4E4') +
  # d
  geom_rect(data=data.frame(ID_group = "d"),
            aes(xmin=d_seq[2], xmax=d_seq[3], ymin=y_min, ymax=y_max),
            alpha = 0.5, fill = '#75E4E4') +
  geom_rect(data=data.frame(ID_group = "d"),
            aes(xmin=d_seq[4], xmax=d_seq[5], ymin=y_min, ymax=y_max),
            alpha = 0.5, fill = '#75E4E4') +
  geom_rect(data=data.frame(ID_group = "d"),
            aes(xmin=d_seq[6], xmax=d_seq[7], ymin=y_min, ymax=y_max),
            alpha = 0.5, fill = '#75E4E4') +
  geom_rect(data=data.frame(ID_group = "d"),
            aes(xmin=d_seq[8], xmax=d_seq[9], ymin=y_min, ymax=y_max),
            alpha = 0.5, fill = '#75E4E4') +
  geom_rect(data=data.frame(ID_group = "d"),
            aes(xmin=d_seq[10], xmax=d_seq[11], ymin=y_min, ymax=y_max),
            alpha = 0.5, fill = '#75E4E4') +
  geom_rect(data=data.frame(ID_group = "d"),
            aes(xmin=d_seq[12], xmax=d_seq[13], ymin=y_min, ymax=y_max),
            alpha = 0.5, fill = '#75E4E4') +
  geom_rect(data=data.frame(ID_group = "d"),
            aes(xmin=d_seq[14], xmax=d_seq[15], ymin=y_min, ymax=y_max),
            alpha = 0.5, fill = '#75E4E4') +
# VdR Regulation
  # b
  geom_rect(data=data.frame(ID_group = "b"),
            aes(xmin=b_seq[2], xmax=b_seq[3], ymin=y_min, ymax=y_max),
            alpha = 0.5, fill = '#C15757') +
  geom_rect(data=data.frame(ID_group = "b"),
            aes(xmin=b_seq[4], xmax=b_seq[5], ymin=y_min, ymax=y_max),
            alpha = 0.5, fill = '#C15757') +
  geom_rect(data=data.frame(ID_group = "b"),
            aes(xmin=b_seq[6], xmax=b_seq[7], ymin=y_min, ymax=y_max),
            alpha = 0.5, fill = '#C15757') +
  geom_rect(data=data.frame(ID_group = "b"),
            aes(xmin=b_seq[8], xmax=b_seq[9], ymin=y_min, ymax=y_max),
            alpha = 0.5, fill = '#C15757') +
  geom_rect(data=data.frame(ID_group = "b"),
            aes(xmin=b_seq[10], xmax=b_seq[11], ymin=y_min, ymax=y_max),
            alpha = 0.5, fill = '#C15757') +
  geom_rect(data=data.frame(ID_group = "b"),
            aes(xmin=b_seq[12], xmax=b_seq[13], ymin=y_min, ymax=y_max),
            alpha = 0.5, fill = '#C15757') +
  # c
  geom_rect(data=data.frame(ID_group = "c"),
            aes(xmin=365*10, xmax=365*50, ymin=y_min, ymax=y_max),
            alpha = 0.5, fill = '#C15757') +
  # d
  geom_rect(data=data.frame(ID_group = "d"),
            aes(xmin=d_seq[1], xmax=d_seq[2], ymin=y_min, ymax=y_max),
            alpha = 0.5, fill = '#C15757') +
  geom_rect(data=data.frame(ID_group = "d"),
            aes(xmin=d_seq[3], xmax=d_seq[4], ymin=y_min, ymax=y_max),
            alpha = 0.5, fill = '#C15757') +
  geom_rect(data=data.frame(ID_group = "d"),
            aes(xmin=d_seq[5], xmax=d_seq[6], ymin=y_min, ymax=y_max),
            alpha = 0.5, fill = '#C15757') +
  geom_rect(data=data.frame(ID_group = "d"),
            aes(xmin=d_seq[7], xmax=d_seq[8], ymin=y_min, ymax=y_max),
            alpha = 0.5, fill = '#C15757') +
  geom_rect(data=data.frame(ID_group = "d"),
            aes(xmin=d_seq[9], xmax=d_seq[10], ymin=y_min, ymax=y_max),
            alpha = 0.5, fill = '#C15757') +
   geom_rect(data=data.frame(ID_group = "d"),
            aes(xmin=d_seq[11], xmax=d_seq[12], ymin=y_min, ymax=y_max),
            alpha = 0.5, fill = '#C15757') +
   geom_rect(data=data.frame(ID_group = "d"),
            aes(xmin=d_seq[13], xmax=d_seq[14], ymin=y_min, ymax=y_max),
            alpha = 0.5, fill = '#C15757') +
  # e
  geom_rect(data=data.frame(ID_group = "e"),
            aes(xmin=365*10, xmax=365*50, ymin=y_min, ymax=y_max),
            alpha = 0.5, fill = '#C15757')
```


```{r}
df_join_VVd_temp <-bind_rows(
  list(df_plot_0.0_VVd,
       df_plot_500.20_VVd,
       df_plot_250.20_VVd,
       df_plot_250.7.5_VVd,
       df_plot_50.7.5_VVd),
  .id = "ID_group_num")
df_join_VVd <- df_join_VVd_temp  %>% mutate(Species = ifelse(Species == "dead_Voles", "Voles dead", Species))

plot_join_VVd <- plot_join + 
  geom_line(data = df_join_VVd,
            aes(x = time, y = ratioVar, color = Species), alpha = 0.5) +
  facet_wrap(~ID_group, ncol = 1)

plot_join_VVd
```

```{r}
df_join_MF <-bind_rows(
  list(df_plot_0.0_MF,
       df_plot_500.20_MF,
       df_plot_250.20_MF,
       df_plot_250.7.5_MF,
       df_plot_50.7.5_MF),
  .id = "ID_group_num")

plot_join_MF <- plot_join +
  geom_line(data = df_join_MF,
            aes(x = time, y = ratioVar, color = Species), alpha  = 0.5) +
  facet_wrap(~ID_group, ncol = 1)

plot_join_MF
```



```{r}
plot_join <- grid.arrange(plot_join_MF,
             plot_join_VVd,
             ncol = 2)
ggsave(filename = "../manuscript/img/plot_join_MF.png", plot = plot_join_MF,
       width = 7, height = 9)
ggsave(filename = "../manuscript/img/plot_join_VVd.png", plot = plot_join_VVd,
       width = 7, height = 9)
ggsave(filename = "../manuscript/img/plot_join.png", plot = plot_join,
       width = 9, height = 7)
```

## Without foxes 

### Foxes and Mustelids


```{r}
## INITIAL VALUE
# scale_fun_F <- function(df){
#   df[df$time == 0, "D.F_"]
# }
# scale_fun_M <- function(df){
#   df[df$time == 0, "D.M_"]
# }
## SCALE WITH MAXIMAL
scale_fun_F <- function(df){
  max(df$D.F_)
}
scale_fun_M <- function(df){
  max(df$D.M_)
}
```


```{r}
df_tab <- as.data.frame(model.output_0.0_0F) %>%
  select(time, D.F_, D.M_) %>%
  mutate(group = "0.0",
         ID_group = "a")
D.F_scale_0.0 = scale_fun_F(df_tab)
D.M_scale_0.0 = scale_fun_M(df_tab)

df_tab$Foxes = df_tab$D.F_ / D.F_scale_0.0
df_tab$Mustelids = df_tab$D.M_ / D.M_scale_0.0

plot(df_tab$time, df_tab$Foxes)
plot(df_tab$time, df_tab$Mustelids)

df_plot_0.0_MF <- df_tab %>%
  gather(Species, ratioVar, c('Foxes', 'Mustelids'))

plot_0.0_MF <- ggplot(data = df_plot_0.0_MF) + theme_minimal() +
  scale_x_continuous(
      breaks = seq(0,max(times),length=11),
      labels=round(seq(0,max(times)/365,length=11),1),
      name="time in year")+
  scale_color_manual(values = c("black", "grey70")) +
  labs(y = "Rate of variation of densities") +
  geom_line(aes(x = time, y = ratioVar, color = Species))
plot_0.0_MF
```

```{r}
df_tab <- as.data.frame(model.output_500.20_0F) %>%
  select(time, D.F_, D.M_) %>%
  mutate(group = "500.20",
         ID_group = "b")
D.F_scale_500.20 = scale_fun_F(df_tab)
D.M_scale_500.20 = scale_fun_M(df_tab)

df_tab$Foxes = df_tab$D.F_ / D.F_scale_500.20
df_tab$Mustelids = df_tab$D.M_ / D.M_scale_500.20

plot(df_tab$time, df_tab$Foxes)
plot(df_tab$time, df_tab$Mustelids)

df_plot_500.20_MF <- df_tab %>%
  gather(Species, ratioVar, c('Foxes', 'Mustelids'))

plot_500.20_MF <- ggplot(data = df_plot_500.20_MF) + theme_minimal() +
  scale_x_continuous(
      breaks = seq(0,max(times),length=11),
      labels=round(seq(0,max(times)/365,length=11),1),
      name="time in year")+
  scale_color_manual(values = c("black", "grey70")) +
  labs(y = "Rate of variation of densities") +
  geom_line(aes(x = time, y = ratioVar, color = Species))
plot_500.20_MF
```


```{r}
df_tab <- as.data.frame(model.output_250.20_0F) %>%
  select(time, D.F_, D.M_) %>%
  mutate(group = "250.20",
         ID_group = "c")
D.F_scale_250.20 = scale_fun_F(df_tab)
D.M_scale_250.20 = scale_fun_M(df_tab)

df_tab$Foxes = df_tab$D.F_ / D.F_scale_250.20
df_tab$Mustelids = df_tab$D.M_ / D.M_scale_250.20

plot(df_tab$time, df_tab$Foxes)
plot(df_tab$time, df_tab$Mustelids)

df_plot_250.20_MF <- df_tab %>%
  gather(Species, ratioVar, c('Foxes', 'Mustelids'))

plot_250.20_MF <- ggplot(data = df_plot_250.20_MF) + theme_minimal() +
  scale_x_continuous(
      breaks = seq(0,max(times),length=11),
      labels=round(seq(0,max(times)/365,length=11),1),
      name="time in year")+
  scale_color_manual(values = c("black", "grey70")) +
  labs(y = "Rate of variation of densities") +
  geom_line(aes(x = time, y = ratioVar, color = Species))
plot_250.20_MF
```


```{r}
df_tab <- as.data.frame(model.output_250.7.5_0F) %>%
  select(time, D.F_, D.M_) %>%
  mutate(group = "250.7.5",
         ID_group = "d")
D.F_scale_250.7.5 = scale_fun_F(df_tab)
D.M_scale_250.7.5 = scale_fun_M(df_tab)

df_tab$Foxes = df_tab$D.F_ / D.F_scale_250.7.5
df_tab$Mustelids = df_tab$D.M_ / D.M_scale_250.7.5

plot(df_tab$time, df_tab$Foxes)
plot(df_tab$time, df_tab$Mustelids)

df_plot_250.7.5_MF <- df_tab %>%
  gather(Species, ratioVar, c('Foxes', 'Mustelids'))

plot_250.7.5_MF <- ggplot(data = df_plot_250.7.5_MF) + theme_minimal() +
  scale_x_continuous(
      breaks = seq(0,max(times),length=11),
      labels=round(seq(0,max(times)/365,length=11),1),
      name="time in year")+
  scale_color_manual(values = c("black", "grey70")) +
  labs(y = "Rate of variation of densities") +
  geom_line(aes(x = time, y = ratioVar, color = Species))
plot_250.7.5_MF
```

```{r}
df_tab <- as.data.frame(model.output_50.7.5_0F) %>%
  select(time, D.F_, D.M_) %>%
  mutate(group = "50.7.5",
         ID_group = "e")
D.F_scale_50.7.5 = scale_fun_F(df_tab)
D.M_scale_50.7.5 = scale_fun_M(df_tab)

df_tab$Foxes = df_tab$D.F_ / D.F_scale_50.7.5
df_tab$Mustelids = df_tab$D.M_ / D.M_scale_50.7.5

plot(df_tab$time, df_tab$Foxes)
plot(df_tab$time, df_tab$Mustelids)

df_plot_50.7.5_MF <- df_tab %>%
  gather(Species, ratioVar, c('Foxes', 'Mustelids'))

plot_50.7.5_MF <- ggplot(data = df_plot_50.7.5_MF) + theme_minimal() +
  scale_x_continuous(
      breaks = seq(0,max(times),length=11),
      labels=round(seq(0,max(times)/365,length=11),1),
      name="time in year")+
  scale_color_manual(values = c("black", "grey70")) +
  labs(y = "Rate of variation of densities") +
  geom_line(aes(x = time, y = ratioVar, color = Species))
plot_50.7.5_MF
```

### Vole and Dead Vole

```{r}
## INITIAL VALUE
# scale_fun_Vd <- function(df){
#   df[df$time == 0, "D.Vd_"]
# }
# scale_fun_V <- function(df){
#   df[df$time == 0, "D.V_"]
# }
## SCALE WITH VAXIVAL
scale_fun_Vd <- function(df){
  max(df$D.Vd_)
}
scale_fun_V <- function(df){
  max(df$D.V_)
}
```



```{r}
df_tab <- as.data.frame(model.output_0.0_0F) %>%
  select(time, D.Vd_, D.V_) %>%
  mutate(group = "0.0",
         ID_group = "a")
D.Vd_scale_0.0 = scale_fun_Vd(df_tab)
D.V_scale_0.0 = scale_fun_V(df_tab)

df_tab$dead_Voles = df_tab$D.Vd_ / D.Vd_scale_0.0
df_tab$Voles = df_tab$D.V_ / D.V_scale_0.0

plot(df_tab$time, df_tab$Voles)
plot(df_tab$time, df_tab$Voles)

df_plot_0.0_VVd <- df_tab %>%
  gather(Species, ratioVar, c('dead_Voles', 'Voles'))

plot_0.0_VVd <- ggplot(data = df_plot_0.0_VVd) + theme_minimal() +
  scale_x_continuous(
      breaks = seq(0,max(times),length=11),
      labels=round(seq(0,max(times)/365,length=11),1),
      name="time in year")+
  scale_color_manual(values = c("black", "grey70")) +
  labs(y = "Rate of variation of densities") +
  geom_line(aes(x = time, y = ratioVar, color = Species))
plot_0.0_VVd
```

```{r}
df_tab <- as.data.frame(model.output_500.20_0F) %>%
  select(time, D.Vd_, D.V_) %>%
  mutate(group = "500.20",
         ID_group = "b")
D.Vd_scale_500.20 = scale_fun_Vd(df_tab)
D.V_scale_500.20 = scale_fun_V(df_tab)

df_tab$dead_Voles = df_tab$D.Vd_ / D.Vd_scale_500.20
df_tab$Voles = df_tab$D.V_ / D.V_scale_500.20

plot(df_tab$time, df_tab$dead_Voles)
plot(df_tab$time, df_tab$Voles)

df_plot_500.20_VVd <- df_tab %>%
  gather(Species, ratioVar, c('dead_Voles', 'Voles'))

plot_500.20_VVd <- ggplot(data = df_plot_500.20_VVd) + theme_minimal() +
  scale_x_continuous(
      breaks = seq(0,max(times),length=11),
      labels=round(seq(0,max(times)/365,length=11),1),
      name="time in year")+
  scale_color_manual(values = c("black", "grey70")) +
  labs(y = "Rate of variation of densities") +
  geom_line(aes(x = time, y = ratioVar, color = Species))
plot_500.20_VVd
```


```{r}
df_tab <- as.data.frame(model.output_250.20_0F) %>%
  select(time, D.Vd_, D.V_) %>%
  mutate(group = "250.20",
         ID_group = "c")
D.Vd_scale_250.20 = scale_fun_Vd(df_tab)
D.V_scale_250.20 = scale_fun_V(df_tab)

df_tab$dead_Voles = df_tab$D.Vd_ / D.Vd_scale_250.20
df_tab$Voles = df_tab$D.V_ / D.V_scale_250.20

plot(df_tab$time, df_tab$dead_Voles)
plot(df_tab$time, df_tab$Voles)

df_plot_250.20_VVd <- df_tab %>%
  gather(Species, ratioVar, c('dead_Voles', 'Voles'))

plot_250.20_VVd <- ggplot(data = df_plot_250.20_VVd) + theme_minimal() +
  scale_x_continuous(
      breaks = seq(0,max(times),length=11),
      labels=round(seq(0,max(times)/365,length=11),1),
      name="time in year")+
  scale_color_manual(values = c("black", "grey70")) +
  labs(y = "Rate of variation of densities") +
  geom_line(aes(x = time, y = ratioVar, color = Species))
plot_250.20_VVd
```


```{r}
df_tab <- as.data.frame(model.output_250.7.5_0F) %>%
  select(time, D.Vd_, D.V_) %>%
  mutate(group = "250.7.5",
         ID_group = "d")
D.Vd_scale_250.7.5 = scale_fun_Vd(df_tab)
D.V_scale_250.7.5 = scale_fun_V(df_tab)

df_tab$dead_Voles = df_tab$D.Vd_ / D.Vd_scale_250.7.5
df_tab$Voles = df_tab$D.V_ / D.V_scale_250.7.5

plot(df_tab$time, df_tab$dead_Voles)
plot(df_tab$time, df_tab$Voles)

df_plot_250.7.5_VVd <- df_tab %>%
  gather(Species, ratioVar, c('dead_Voles', 'Voles'))

plot_250.7.5_VVd <- ggplot(data = df_plot_250.7.5_VVd) + theme_minimal() +
  scale_x_continuous(
      breaks = seq(0,max(times),length=11),
      labels=round(seq(0,max(times)/365,length=11),1),
      name="time in year")+
  scale_color_manual(values = c("black", "grey70")) +
  labs(y = "Rate of variation of densities") +
  geom_line(aes(x = time, y = ratioVar, color = Species))
plot_250.7.5_VVd
```

```{r}
df_tab <- as.data.frame(model.output_50.7.5_0F) %>%
  select(time, D.Vd_, D.V_) %>%
  mutate(group = "50.7.5",
         ID_group = "e")
D.Vd_scale_50.7.5 = scale_fun_Vd(df_tab)
D.V_scale_50.7.5 = scale_fun_V(df_tab)

df_tab$dead_Voles = df_tab$D.Vd_ / D.Vd_scale_50.7.5
df_tab$Voles = df_tab$D.V_ / D.V_scale_50.7.5

plot(df_tab$time, df_tab$dead_Voles)
plot(df_tab$time, df_tab$Voles)

df_plot_50.7.5_VVd <- df_tab %>%
  gather(Species, ratioVar, c('dead_Voles', 'Voles'))

plot_50.7.5_VVd <- ggplot(data = df_plot_50.7.5_VVd) + theme_minimal() +
  scale_x_continuous(
      breaks = seq(0,max(times),length=11),
      labels=round(seq(0,max(times)/365,length=11),1),
      name="time in year")+
  scale_color_manual(values = c("black", "grey70")) +
  labs(y = "Rate of variation of densities") +
  geom_line(aes(x = time, y = ratioVar, color = Species))
plot_50.7.5_VVd
```

### Plots and join plot


```{r}
# legend.position = c(.5, .5))
# z + theme(legend.background = element_rect(colour = "black")
plot_join <- ggplot() +
  theme_minimal() +
  theme(legend.position = c(0.13, 0.93), # c(0,0) bottom left, c(1,1) top-right.
        legend.background = element_rect(fill = "#ffffffaa", colour = NA),
        legend.title = element_blank()
  ) +
  # theme(legend.position="none") +
  scale_x_continuous(
      breaks = seq(0,max(times),length=11),
      labels=round(seq(0,max(times)/365,length=11),1),
      name="Time in year")+
  scale_color_manual(values = c("black", "grey50")) +
  labs(y = "Rate of variation of densities") +
  # Buffer
  geom_rect(
    data=data.frame(ID_group = c("a", "b", "c", "d", "e")),
    aes(xmin=0, xmax=365*10, ymin=-Inf, ymax=Inf), 
    alpha = 0.5, fill = 'grey')

y_min = -Inf # 1 
y_max = Inf # 1.2
# 
# b_seq = 365*c(10,   14.5,16.1,    21.2,22.9,   28,29.5,   34.9,36.5,   41.6,43.3,   48.3,50)
# d_seq = 365*c(10,12.2,  14.8,17,  20.5,24, 27.2,30.4,   33.2,35.6,   39,42.7,  45.5,47.9,  50)
# # VR Regulation
# plot_join <- plot_join +
#   geom_rect(data=data.frame(ID_group = "a"),
#             aes(xmin=365*10, xmax=365*50, ymin=y_min, ymax=y_max),
#             alpha = 0.5, fill = '#75E4E4') +
#   # b
#   geom_rect(data=data.frame(ID_group = "b"),
#             aes(xmin=b_seq[1], xmax=b_seq[2], ymin=y_min, ymax=y_max),
#             alpha = 0.5, fill = '#75E4E4') +
#   geom_rect(data=data.frame(ID_group = "b"),
#             aes(xmin=b_seq[3], xmax=b_seq[4], ymin=y_min, ymax=y_max),
#             alpha = 0.5, fill = '#75E4E4') +
#   geom_rect(data=data.frame(ID_group = "b"),
#             aes(xmin=b_seq[5], xmax=b_seq[6], ymin=y_min, ymax=y_max),
#             alpha = 0.5, fill = '#75E4E4') +
#   geom_rect(data=data.frame(ID_group = "b"),
#             aes(xmin=b_seq[7], xmax=b_seq[8], ymin=y_min, ymax=y_max),
#             alpha = 0.5, fill = '#75E4E4') +
#   geom_rect(data=data.frame(ID_group = "b"),
#             aes(xmin=b_seq[9], xmax=b_seq[10], ymin=y_min, ymax=y_max),
#             alpha = 0.5, fill = '#75E4E4') +
#   geom_rect(data=data.frame(ID_group = "b"),
#             aes(xmin=b_seq[11], xmax=b_seq[12], ymin=y_min, ymax=y_max),
#             alpha = 0.5, fill = '#75E4E4') +
#   # d
#   geom_rect(data=data.frame(ID_group = "d"),
#             aes(xmin=d_seq[2], xmax=d_seq[3], ymin=y_min, ymax=y_max),
#             alpha = 0.5, fill = '#75E4E4') +
#   geom_rect(data=data.frame(ID_group = "d"),
#             aes(xmin=d_seq[4], xmax=d_seq[5], ymin=y_min, ymax=y_max),
#             alpha = 0.5, fill = '#75E4E4') +
#   geom_rect(data=data.frame(ID_group = "d"),
#             aes(xmin=d_seq[6], xmax=d_seq[7], ymin=y_min, ymax=y_max),
#             alpha = 0.5, fill = '#75E4E4') +
#   geom_rect(data=data.frame(ID_group = "d"),
#             aes(xmin=d_seq[8], xmax=d_seq[9], ymin=y_min, ymax=y_max),
#             alpha = 0.5, fill = '#75E4E4') +
#   geom_rect(data=data.frame(ID_group = "d"),
#             aes(xmin=d_seq[10], xmax=d_seq[11], ymin=y_min, ymax=y_max),
#             alpha = 0.5, fill = '#75E4E4') +
#   geom_rect(data=data.frame(ID_group = "d"),
#             aes(xmin=d_seq[12], xmax=d_seq[13], ymin=y_min, ymax=y_max),
#             alpha = 0.5, fill = '#75E4E4') +
#   geom_rect(data=data.frame(ID_group = "d"),
#             aes(xmin=d_seq[14], xmax=d_seq[15], ymin=y_min, ymax=y_max),
#             alpha = 0.5, fill = '#75E4E4') +
# # VdR Regulation
#   # b
#   geom_rect(data=data.frame(ID_group = "b"),
#             aes(xmin=b_seq[2], xmax=b_seq[3], ymin=y_min, ymax=y_max),
#             alpha = 0.5, fill = '#C15757') +
#   geom_rect(data=data.frame(ID_group = "b"),
#             aes(xmin=b_seq[4], xmax=b_seq[5], ymin=y_min, ymax=y_max),
#             alpha = 0.5, fill = '#C15757') +
#   geom_rect(data=data.frame(ID_group = "b"),
#             aes(xmin=b_seq[6], xmax=b_seq[7], ymin=y_min, ymax=y_max),
#             alpha = 0.5, fill = '#C15757') +
#   geom_rect(data=data.frame(ID_group = "b"),
#             aes(xmin=b_seq[8], xmax=b_seq[9], ymin=y_min, ymax=y_max),
#             alpha = 0.5, fill = '#C15757') +
#   geom_rect(data=data.frame(ID_group = "b"),
#             aes(xmin=b_seq[10], xmax=b_seq[11], ymin=y_min, ymax=y_max),
#             alpha = 0.5, fill = '#C15757') +
#   geom_rect(data=data.frame(ID_group = "b"),
#             aes(xmin=b_seq[12], xmax=b_seq[13], ymin=y_min, ymax=y_max),
#             alpha = 0.5, fill = '#C15757') +
#   # c
#   geom_rect(data=data.frame(ID_group = "c"),
#             aes(xmin=365*10, xmax=365*50, ymin=y_min, ymax=y_max),
#             alpha = 0.5, fill = '#C15757') +
#   # d
#   geom_rect(data=data.frame(ID_group = "d"),
#             aes(xmin=d_seq[1], xmax=d_seq[2], ymin=y_min, ymax=y_max),
#             alpha = 0.5, fill = '#C15757') +
#   geom_rect(data=data.frame(ID_group = "d"),
#             aes(xmin=d_seq[3], xmax=d_seq[4], ymin=y_min, ymax=y_max),
#             alpha = 0.5, fill = '#C15757') +
#   geom_rect(data=data.frame(ID_group = "d"),
#             aes(xmin=d_seq[5], xmax=d_seq[6], ymin=y_min, ymax=y_max),
#             alpha = 0.5, fill = '#C15757') +
#   geom_rect(data=data.frame(ID_group = "d"),
#             aes(xmin=d_seq[7], xmax=d_seq[8], ymin=y_min, ymax=y_max),
#             alpha = 0.5, fill = '#C15757') +
#   geom_rect(data=data.frame(ID_group = "d"),
#             aes(xmin=d_seq[9], xmax=d_seq[10], ymin=y_min, ymax=y_max),
#             alpha = 0.5, fill = '#C15757') +
#    geom_rect(data=data.frame(ID_group = "d"),
#             aes(xmin=d_seq[11], xmax=d_seq[12], ymin=y_min, ymax=y_max),
#             alpha = 0.5, fill = '#C15757') +
#    geom_rect(data=data.frame(ID_group = "d"),
#             aes(xmin=d_seq[13], xmax=d_seq[14], ymin=y_min, ymax=y_max),
#             alpha = 0.5, fill = '#C15757') +
#   # e
#   geom_rect(data=data.frame(ID_group = "e"),
#             aes(xmin=365*10, xmax=365*50, ymin=y_min, ymax=y_max),
#             alpha = 0.5, fill = '#C15757')
```


```{r}
df_join_VVd_temp <-bind_rows(
  list(df_plot_0.0_VVd,
       df_plot_500.20_VVd,
       df_plot_250.20_VVd,
       df_plot_250.7.5_VVd,
       df_plot_50.7.5_VVd),
  .id = "ID_group_num")
df_join_VVd <- df_join_VVd_temp  %>% mutate(Species = ifelse(Species == "dead_Voles", "Voles dead", Species))

plot_join_VVd <- plot_join + 
  geom_line(data = df_join_VVd,
            aes(x = time, y = ratioVar, color = Species), alpha = 0.5) +
  facet_wrap(~ID_group, ncol = 1)

plot_join_VVd
```

```{r}
df_join_MF <-bind_rows(
  list(df_plot_0.0_MF,
       df_plot_500.20_MF,
       df_plot_250.20_MF,
       df_plot_250.7.5_MF,
       df_plot_50.7.5_MF),
  .id = "ID_group_num")

plot_join_MF <- plot_join +
  geom_line(data = df_join_MF,
            aes(x = time, y = ratioVar, color = Species), alpha = 0.5) +
  facet_wrap(~ID_group, ncol = 1)

plot_join_MF
```


```{r}
plot_join <- grid.arrange(plot_join_MF,
             plot_join_VVd,
             ncol = 2)
ggsave(filename = "../manuscript/img/plot_join_MF_0F.png", plot = plot_join_MF,
       width = 7, height = 9)
ggsave(filename = "../manuscript/img/plot_join_VVd_0F.png", plot = plot_join_VVd,
       width = 7, height = 9)
ggsave(filename = "../manuscript/img/plot_join_0F.png", plot = plot_join,
       width = 9, height = 7)
```

# PLOT ROLLING MEANS

```{r}
library(zoo)
widthRollMean = 365/2  * length(times)/ (50*365)

df_rollMean <- function(x){
  data.frame(x) %>%
  mutate(V_rollMean = rollmean(D.V_, widthRollMean, fill = NA),
         M_rollMean = rollmean(D.M_, widthRollMean, fill = NA),
         F_rollMean = rollmean(D.F_, widthRollMean, fill = NA)) %>%
  select(time, D.V_, D.M_, D.F_, V_rollMean, M_rollMean, F_rollMean) %>%
  gather("Measure", "Density", -time)  %>%
  mutate(Population = ifelse(grepl("V_", Measure), "V",
                             ifelse(grepl("M_", Measure), "M",
                                    ifelse(grepl("F_", Measure), "F", NA))),
         type = ifelse(grepl("rollMean", Measure), "rollMean", "density"))
}

plt_rollMean =  ggplot() + theme_minimal() + 
  theme_minimal() +
  scale_color_manual(values = c("black", "blue")) +
  theme(legend.position="top")+
  scale_x_continuous(
    breaks = seq(0,max(times),length=11),
    labels=round(seq(0,max(times)/365,length=11),1),
    name="time in year")
```

## With foxes

```{r}
plt_roll_0.0 <-  plt_rollMean +
  geom_line(data = df_rollMean(model.output_0.0),
            aes(x = time, y = Density, color = type)) + 
  facet_wrap(~ Population, ncol = 1, scales = "free")
plt_roll_0.0

plt_roll_500.20 <-  plt_rollMean +
  geom_line(data = df_rollMean(model.output_500.20),
            aes(x = time, y = Density, color = type)) + 
  facet_wrap(~ Population, ncol = 1, scales = "free")
plt_roll_500.20

plt_roll_250.20 <-  plt_rollMean +
  geom_line(data = df_rollMean(model.output_250.20),
            aes(x = time, y = Density, color = type)) + 
  facet_wrap(~ Population, ncol = 1, scales = "free")
plt_roll_250.20

plt_roll_250.7.5 <- plt_rollMean +
  geom_line(data = df_rollMean(model.output_250.7.5),
            aes(x = time, y = Density, color = type)) + 
  facet_wrap(~ Population, ncol = 1, scales = "free")
plt_roll_250.7.5

plt_roll_50.7.5 <- plt_rollMean +
  geom_line(data = df_rollMean(model.output_50.7.5),
            aes(x = time, y = Density, color = type)) + 
  facet_wrap(~ Population, ncol = 1, scales = "free")
plt_roll_50.7.5

ggsave(filename = "../manuscript/img/plt_roll_0.0.svg",
       plot = plt_roll_0.0,
       width = 7, height = 5)
ggsave(filename = "../manuscript/img/plt_roll_500.20.svg",
       plot = plt_roll_500.20,
       width = 7, height = 5)
ggsave(filename = "../manuscript/img/plt_roll_250.20.svg",
       plot = plt_roll_250.20,
       width = 7, height = 5)
ggsave(filename = "../manuscript/img/plt_roll_250.7.5.svg",
       plot = plt_roll_250.7.5,
       width = 7, height = 5)
ggsave(filename = "../manuscript/img/plt_roll_50.7.5.svg",
       plot = plt_roll_50.7.5,
       width = 7, height = 5)
```

### Repartition of ingestion in mustelids and foxes

```{r,warning=FALSE, cache=TRUE}
df = table_df(model.output_250.7.5)
df = filter(df, time >=15*365, time <=25*365)
df.Nbr.ingest=Nbr.ingest(df,params,group.num=1)

p.ingest=plotIngest(df.Nbr.ingest)

ingestion.mustelids=p.ingest[[1]]
ingestion.foxes=p.ingest[[2]]

plt_feed_ingest_VVd = grid.arrange(ingestion.mustelids,ingestion.foxes,nrow=2)

ggsave(filename = "../manuscript/img/plt_feed_ingest_250.7.5_VVd.svg",
       plot = plt_feed_ingest_VVd,
       width = 7, height = 8)
```

### Repartition of mortality in Voles and Mustelids

```{r,warning=FALSE, cache=TRUE}
df.Nbr.mortality=Nbr.mortality(df,params,group.num=1)

p.mortality=plotMortality(df.Nbr.mortality)

mortality.voles=p.mortality[[1]]
mortality.mustelids=p.mortality[[2]]

plt_feed_ingest_MF = grid.arrange(mortality.voles,mortality.mustelids,nrow=2)

ggsave(filename = "../manuscript/img/plt_feed_ingest_250.7.5_MF.svg",
       plot = plt_feed_ingest_MF,
       width = 7, height = 8)
```


## Without foxes

```{r}
plt_roll_0.0_0F <- plt_rollMean +
  geom_line(data = df_rollMean(model.output_0.0_0F),
            aes(x = time, y = Density, color = type)) + 
  facet_wrap(~ Population, ncol = 1, scales = "free", cols = 1)
plt_roll_0.0_0F

plt_roll_500.20_0F <- plt_rollMean +
  geom_line(data = df_rollMean(model.output_500.20_0F),
            aes(x = time, y = Density, color = type)) + 
  facet_wrap(~ Population, ncol = 1, scales = "free", cols = 1)
plt_roll_500.20_0F

plt_roll_250.20_0F <- plt_rollMean +
  geom_line(data = df_rollMean(model.output_250.20_0F),
            aes(x = time, y = Density, color = type)) + 
  facet_wrap(~ Population, ncol = 1, scales = "free")
plt_roll_250.20_0F

plt_roll_250.7.5_0F <- plt_rollMean +
  geom_line(data = df_rollMean(model.output_250.7.5_0F),
            aes(x = time, y = Density, color = type)) + 
  facet_wrap(~ Population, ncol = 1, scales = "free")
plt_roll_250.7.5_0F

plt_roll_50.7.5_0F <- plt_rollMean +
  geom_line(data = df_rollMean(model.output_50.7.5_0F),
            aes(x = time, y = Density, color = type)) + 
  facet_wrap(~ Population, ncol = 1, scales = "free")
plt_roll_50.7.5_0F

ggsave(filename = "../manuscript/img/plt_roll_0.0_0F.svg",
       plot = plt_roll_0.0_0F,
       width = 7, height = 5)
ggsave(filename = "../manuscript/img/plt_roll_500.20_0F.svg",
       plot = plt_roll_500.20_0F,
       width = 7, height = 5)
ggsave(filename = "../manuscript/img/plt_roll_250.20_0F.svg",
       plot = plt_roll_250.20_0F,
       width = 7, height = 5)
ggsave(filename = "../manuscript/img/plt_roll_250.7.5_0F.svg",
       plot = plt_roll_250.7.5_0F,
       width = 7, height = 5)
ggsave(filename = "../manuscript/img/plt_roll_50.7.5_0F.svg",
       plot = plt_roll_50.7.5_0F,
       width = 7, height = 5)
```



### Repartition of ingestion in mustelids and foxes

```{r,warning=FALSE, cache=TRUE}
df = table_df(model.output_250.7.5_0F)
df = filter(df, time >=15*365, time <=25*365)
df.Nbr.ingest=Nbr.ingest(df,params,group.num=1)

p.ingest=plotIngest(df.Nbr.ingest)

ingestion.mustelids=p.ingest[[1]]
ingestion.foxes=p.ingest[[2]]

plt_feed_ingest_VVd = grid.arrange(ingestion.mustelids,ingestion.foxes,nrow=2)

ggsave(filename = "../manuscript/img/plt_feed_ingest_VVd_250.7.5_0F.svg",
       plot = plt_feed_ingest_VVd,
       width = 7, height = 5)
```

### Repartition of mortality in Voles and Mustelids

```{r,warning=FALSE, cache=TRUE}
df.Nbr.mortality=Nbr.mortality(df,params,group.num=1)

p.mortality=plotMortality(df.Nbr.mortality)

mortality.voles=p.mortality[[1]]
mortality.mustelids=p.mortality[[2]]

plt_feed_ingest_MF = grid.arrange(mortality.voles,mortality.mustelids,nrow=2)

ggsave(filename = "../manuscript/img/plt_feed_ingest_MF_250.7.5_0F.svg",
       plot = plt_feed_ingest_MF,
       width = 7, height = 5)
```
